---
title: "Getting started with R Exercises"
learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(gradethis)
library(dplyr)
tutorial_options(exercise.checker= gradethis::grade_learnr)
gradethis::gradethis_setup()
knitr::opts_chunk$set(echo = FALSE)
```

```{r cache=FALSE}
knitr::read_chunk('solution_1.R')
```

#### **<span style="color: orange;">Exercise 1</span>** {-}
You can use R like a calculator.  Try typing `2+8` into the **R console**.
```{r exercise_1, exercise = TRUE}

```

#### **<span style="color: orange;">Exercise 2</span>** {-}
What command is used to install the tidyverse package in R?    
```{r exercise_2, exercise = TRUE}

```
#### **<span style="color: orange;">Exercise 3</span>** {-}
What command is used to load the tidyverse package in R?    
```{r exercise_3, exercise = TRUE}

```

#### **<span style="color: orange;">Exercise 4</span>** {-}
How would you inspect the content of the cells in 4th column, rows 3 to 5 of the icebio data set?
```{r exercise_4, exercise = TRUE}

```

#### **<span style="color: orange;">Exercise 5</span>** {-}
Using the table function, how many women are in the data collected between 2002 and 2005?
```{r exercise_5, exercise = TRUE}

```
#### **<span style="color: orange;">Exercise 6</span>** {-}
Using the ftable function, how many men are are from northern Ireland in the data collected between 1990 and 1994?
```{r exercise_6, exercise = TRUE}

```
#### **<span style="color: orange;">Exercise 7</span>** {-}
Using the data called icebio, create a new data set called ICE_Ire_ordered and arrange the data in descending order by the number of words that each speaker has uttered. Who is the speaker (filename) with the highest word count?

```{r exercise_7, exercise = TRUE}

```

#globals
```{r}
icebio <- read.delim("https://slcladal.github.io/data/BiodataIceIreland.txt", 
                      sep = "\t", header = T)
```

```{r}
ICE_Ire_ordered <- icebio %>%
  dplyr::arrange(-word.count)
```

#check
```{r exercise_1-check}
grade_code()
```

```{r exercise_2-check}
grade_code()
```

```{r exercise_3-check}
grade_code()
```

```{r exercise_4-check}
grade_code()
```
```{r exercise_5-check}
grade_code()
```
```{r exercise_6-check}
grade_code()
```

```{r exercise_7-check}
grade_code()
```


#hints
```{r exercise_1-hint-1}
x + y = 10
what is x and y? 
```

```{r exercise_2-hint-1}
Did you remember to add quotation marks for the package name?
```

```{r exercise_2-hint-2}
install.packages("____")
```

```{r exercise_3-hint-1}
library(____) 
```

```{r exercise_4-hint-1}
icebio[ , ]
```

```{r exercise_4-hint-2}
icebio[x:y, z]
what is x,y and z?
```

```{r exercise_5-hint-1}
table(icebio$___, icebio$___)
fill in the blanks
```

```{r exercise_5-hint-2}
table(icebio$date, icebio$sex)
```

```{r exercise_6-hint-1}
ftable(icebio$___, icebio$___, icebio$___)
fill in the blanks
```

```{r exercise_6-hint-2}
ftable(icebio$date, icebio$sex, icebio$zone)
```

```{r exercise_7-hint-1}
Put this into the console and run code.
head(ICE_Ire_ordered)
```

#solutions:
```{r exercise_1-solution}
10
```

```{r exercise_2-solution}
install.packages("tidyverse")
```

```{r exercise_3-solution}
library(tidyverse)
```

```{r exercise_4-solution,  exercise.reveal_solution = FALSE}
icebio[3:5, 4]
```

```{r exercise_5-solution,  exercise.reveal_solution = FALSE}
table(icebio$date, icebio$sex)
```

```{r exercise_6-solution,  exercise.reveal_solution = FALSE}
ftable(icebio$date, icebio$sex, icebio$zone)
```

```{r exercise_7-solution,  exercise.reveal_solution = FALSE}
S2A-037$A
```
